Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-08-04 ms.tex
added info about reference pixels versus no reference pixels.

>>>>

\subsection{Reference Pixels versus No Reference Pixels}
One question to answer is, can background subtraction subtract off noise just as well as reference pixels?
We compare time series on source boxes subtracted by a background box on data that has been reference pixel subtracted and data that has not been reference pixel subtracted.
As before, the background boxes are offset horizontally from the source boxes to best capture 1/f noise.
For the baseline test, with a 2048x256 subarray, the standard deviation was 197.11 ppm with reference pixel correction.
Repeating the experiment with no reference pixel correction, the standard deviation was 198.19 ppm.
This test indicates that horizontally displaced background box is sufficient in removing pre-amp offsets and 1/f noise from the source aperture.
However, for some cases (like NIRCam grism time series), the background subtraction will be done vertically and so side reference pixels will be desired.

If not top reference pixels are available (such as in the 2048x64 subarray test), and only side reference pixels are available, the benefits are similar.
For the 2048x64 1.5 mA test with reset-per-frame, the standard deviation was 326.9 ppm with reference pixel correction and 327.2 ppm without reference pixel correction.
